Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-27 demystify.tex
update

\documentclass[oneside,11pt]{memoir}
\setsecnumdepth{subsection}

@@

\section{References}
\begin{itemize}
    \item \href{https://parentheticallyspeaking.org/articles/us-cs-phd-faq/}{Getting a Computer Science PhD in the USA} by Shriram Krishnamurthi
\end{itemize}

@@

\subsection{References}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

\section{Choosing a Professor}
Obviously, there is no one-size-fit-all answer to this question. The best adviser is the one that you can work well with, i.e., \emph{fits} you.  This is difficult and takes time. Fortunately, unlike many countries that require finding an adviser and research topic before starting the PhD (\S\ref{sec:non-us-differences}), CS PhD programs in the US will typically give you a couple of years to search for advisers and research topics.  This is especially true if you're admitted with TA (\S\ref{sec:ta}), which gives you time to explore and find adviser.

@@

Ultimately, choose a prof. that fits you the most by communicating with them, taking their courses, meeting them, asking them questions, and even talking to their current students. Doing these takes a lot of time and effort, but remember, you will be working with this person for 5+ years, so it is important to try to find the right one.

@@

\subsubsection{References}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and Other Academic Titles}\label{sec:faculty-types}

@@

\subsubsection{References}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{A Note about Emailing Professors} by Yonatan Bisk
\end{itemize}

@@

\chapter{References}

>>>>

\documentclass[oneside,11pt]{memoir}
\setsecnumdepth{subsection}
\setcounter{tocdepth}{3}

@@

\section*{References}
\begin{itemize}
    \item \href{https://parentheticallyspeaking.org/articles/us-cs-phd-faq/}{Getting a Computer Science PhD in the USA} by Shriram Krishnamurthi
\end{itemize}

@@

\subsection*{References}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

\section{Choosing an Advisor}
Obviously, there is no one-size-fit-all answer to this question. The best adviser is the one that you can work well with, i.e., \emph{fits} you.  This is difficult and takes time. Fortunately, unlike many countries that require finding an adviser and research topic before starting the PhD (\S\ref{sec:non-us-differences}), CS PhD programs in the US will typically give you a couple of years to search for advisers and research topics.  This is especially true if you're admitted with TA (\S\ref{sec:ta}), which gives you time to explore and find adviser.

@@

Ultimately, choose a prof. that fits you the most by communicating with them, taking their courses, meeting and asking them questions, and even talking to their current students. It will take time and effort, but remember, you will be working with this person for 5+ years, so it is important to try to find the right one.

@@

\subsubsection*{References}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and Other Academic Titles}\label{sec:faculty-types}

@@

\subsubsection*{References}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{A Note about Emailing Professors} by Yonatan Bisk
\end{itemize}

@@

%\chapter{References}
